---
title: "Eating Out"
author: "Sarah Medina"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## There were two years in which the General Social Survey asked about the frequency of eating out.
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r, eval=TRUE}
GSS <-read.dta(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

## Methods

We will be using the Cat Cat helper file to analyze the two categorical factors Race and the frequency at which they eat out. In order to determine if there is a statistical difference among the various races and the frequency at which they eat out. Additionally, we will use graphical, numerical, and inferential methods to determine if there is a statistical difference between at least two of the races regarding the frequency at which they eat out.

## Graphical Results 

#### Plot barplots tigerstats way

```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```

The bar chart indicates that of the white people about 85 percent eat out and less than 20 percent do not eat out. Furthermore, about 70 percent of black people eat out and 30 percent do not eat out. Lastly, for all other races about 79 percent eat out and about 22 percent do not eat out. It seems that the white people eat out the most, the black people eat out the least, and the other races are in between the white and black people.  


  
### Numerical Summaries  

```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```

The numerical results indicate that 83 percent of white people eat out and that 17 percent of white people do not eat out. Furthermore, 69 percent of the black people eat out while 31 percent do not eat out. Lastly, for all other races 78 percent eat out and and 22 percent do not eat out. It appears that the white people eat out the most followed by the other races and black people eat out the least. 

